Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-03 WSSSPE3/report/WSSSPE3_review.tex
edits to edits
Replied to Dan's note.
changed single quote marks to double for keynote quotes

\definecolor{orange}{rgb}{1.0,0.3,0.0}
\definecolor{violet}{rgb}{0.75,0,1}
\definecolor{darkgreen}{rgb}{0,0.6,0}
\definecolor{cyan}{rgb}{0.2,0.7,0.7}
\definecolor{blueish}{rgb}{0.2,0.2,0.8}

\newcommand{\todo}[1]{{\color{blue}$\blacksquare$~\textsf{[TODO: #1]}}}
\newcommand{\note}[1]{ {\textcolor{blueish}    { ***Note:      #1 }}}
\newcommand{\katznote}[1]{ {\textcolor{magenta}    { ***Dan:      #1 }}}
\newcommand{\clunenote}[1]{ {\textcolor{orange}    { ***Tom:      #1 }}}
\newcommand{\gabnote}[1]{ {\textcolor{cyan}    { ***Gabrielle:     #1 }}}
\newcommand{\nchnote}[1]{  {\textcolor{orange}      { ***Neil: #1 }}}
\newcommand{\manishnote}[1]{  {\textcolor{violet}     { ***Manish: #1 }}}
\newcommand{\davidnote}[1]{  {\textcolor{darkgreen}      { ***David: #1 }}}
\newcommand{\colinnote}[1]{ {\textcolor{red}    {***Colin: #1 }}}
\newcommand{\choinote}[1]{ {\textcolor{orange}    {***Choi: #1 }}}

@@

Turk then moved onto various different definitions of sustainability. His
favorite one was `keeping up with bug reports,' where even if no new features
were added, the software remains sustainable. Another definition of
sustainability Turk mentioned was `adding of new features', or `maintaining the
software for a long period of time' such as the cases of TeX or LaTeX with
community help. A notion Turk heard often at supercomputing conferences was that
sustainable software `continues to work on new architectures'. Yet another
metric was `people continuing to be able to learn how to use and apply the
software'. A funder Turk heard talked about sustainability as `continuing to get
funded'. Turk also recalled that Greg Wilson, among others, said in WSSSPE1.1
that his view of sustainable software was software that `continued to give the
same results over time'. A last measure of sustainability Turk presented was
`the ability to transition between different people developing and using a piece
of software.'

@@

\item \textbf{Lorraine Hwang, Joe Dumit, Alison Fish, Louise Kellogg, Mackenzie
Smith, and Laura Soito: \textit{Software Attribution for Geoscience Applications
in the Computational Infrastructure for Geodynamics}} In a second talk, Lorraine
Hwang mentioned various ways to cite efforts within the framework, including
science papers, code papers, user manuals, and the CIG website. An analysis of
the resulting citations showed that $80\%$ of papers that use CIG codes mention
the code name, and about the same number includes a citation. Only about $20\%$
acknowledge CIG. Within the same sample of papers, about one fifth use an URL to
cite codes (including non-CIG codes), and only about one eighth specify the
version used. Compared to other codes, CIG seems to be much better cited. 
This in part is attribute to requiring that donated software provide a citable paper specified in the User Manual. 
The project is working on tools and methods to generate attribution information automatically.
%This,
%in part, is attributed to suggested citation forms communicated to the
%community, and runtime tools that help collecting a relevant citation list
%automatically.

>>>>

\definecolor{orange}{rgb}{1.0,0.3,0.0}
\definecolor{violet}{rgb}{0.75,0,1}
\definecolor{darkgreen}{rgb}{0,0.6,0}
\definecolor{cyan}{rgb}{0.2,0.7,0.7}
\definecolor{blueish}{rgb}{0.2,0.2,0.8}
\definecolor{darkblue}{rgb}{0.1,0.1,0.9}

\newcommand{\todo}[1]{{\color{blue}$\blacksquare$~\textsf{[TODO: #1]}}}
\newcommand{\note}[1]{ {\textcolor{blueish}    { ***Note:      #1 }}}
\newcommand{\katznote}[1]{ {\textcolor{magenta}    { ***Dan:      #1 }}}
\newcommand{\clunenote}[1]{ {\textcolor{orange}    { ***Tom:      #1 }}}
\newcommand{\gabnote}[1]{ {\textcolor{cyan}    { ***Gabrielle:     #1 }}}
\newcommand{\nchnote}[1]{  {\textcolor{orange}      { ***Neil: #1 }}}
\newcommand{\manishnote}[1]{  {\textcolor{violet}     { ***Manish: #1 }}}
\newcommand{\davidnote}[1]{  {\textcolor{darkgreen}      { ***David: #1 }}}
\newcommand{\colinnote}[1]{ {\textcolor{red}    {***Colin: #1 }}}
\newcommand{\choinote}[1]{ {\textcolor{orange}    {***Choi: #1 }}}
\newcommand{\stevenote}[1]{ {\textcolor{darkblue}    {***Steve: #1 }}}

@@

Turk then moved onto various different definitions of sustainability. His
favorite one was ``keeping up with bug reports,'' where even if no new features
were added, the software remains sustainable. Another definition of
sustainability Turk mentioned was ``adding of new features,'' or ``maintaining the
software for a long period of time'' such as the cases of TeX or LaTeX with
community help. A notion Turk heard often at supercomputing conferences was that
sustainable software ``continues to work on new architectures.'' Yet another
metric was ``people continuing to be able to learn how to use and apply the
software.'' A funder Turk heard talked about sustainability as ``continuing to get
funded.'' Turk also recalled that Greg Wilson, among others, said in WSSSPE1.1
that his view of sustainable software was software that ``continued to give the
same results over time.'' A last measure of sustainability Turk presented was
``the ability to transition between different people developing and using a piece
of software.''

@@

\item \textbf{Lorraine Hwang, Joe Dumit, Alison Fish, Louise Kellogg, Mackenzie
Smith, and Laura Soito: \textit{Software Attribution for Geoscience Applications
in the Computational Infrastructure for Geodynamics}} In a second talk, Lorraine
Hwang mentioned various ways to cite efforts within the framework, including
science papers, code papers, user manuals, and the CIG website. An analysis of
the resulting citations showed that $80\%$ of papers that use CIG codes mention
the code name, and about the same number includes a citation. Only about $20\%$
acknowledge CIG. Within the same sample of papers, about one fifth use an URL to
cite codes (including non-CIG codes), and only about one eighth specify the
version used. Compared to other codes, CIG seems to be much better cited. 
In part, this is attributed to the fact that CIG requires that donated software provide a citable paper specified in the User Manual. 
The project is working on tools and methods to generate attribution information automatically.
%This,
%in part, is attributed to suggested citation forms communicated to the
%community, and runtime tools that help collecting a relevant citation list
%automatically.
